### 2019-10-23 README.Rmd
abstract format, citations, future work
completed paper draft

# Evaluating the Mechanisms for Missing Data in the Enhanced Tuberculosis Surveillance System

@@

The Enhanced Tuberculosis Surveillance (ETS) system is a routine surveillance system that collects data on all notified tuberculosis (TB) cases in England and is routinely used in research. Routine data often has a large amount of missing data which may introduce bias to analyses. This study explores the evidence for associations between missingness in several outcomes and demographic variables. Any such associations may introduce bias if not accounted for.

>>>>

# Exploring Missing Data in the Enhanced Tuberculosis Surveillance System

@@

The Enhanced Tuberculosis Surveillance (ETS) system is a routine surveillance system that collects data on all notified tuberculosis (TB) cases in England and is routinely used in research. Routine data often has a large amount of missing data which may introduce bias to analyses.

## Aim

Explore potential sources of bias from missing data for key outcomes in the ETS system.
